\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-05-15 doc/sw-system.tex
Tutorial, instant feedback

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centerline{
\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}}
\caption{Screenshot of the \sw classification interface.}
\label{fig:interface}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A screenshot of the \sw classification interface (CI) is shown in
\Fref{fig:interface}. The CI is the centrepiece of the \sw website,
\texttt{http://spacewarps.org}; the web application is written in
coffeescript, css and html and follows the general design of others written by
the Zooniverse team.\footnote{The \sw web application code is open source and
can be accessed from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The
focus of the CI is a large display of the current pre-prepared PNG image of
the ``subject'' being inspected.   When the image is clicked on by the
volunteer, a marker symbol appears where the pointer was. Several markers can
be placed.  The next image moves rapidly in from a queue formed at the right
hand side of the screen when the ``Finished marking'' button is pressed. At
the same time, the positions of the markers are written out to the
classification database, in an entry that also stores the ID of the subject,
the username (or IP address) of the volunteer, a timestamp and some other
metadata.

@@

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard,'' a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
features they have seen either before they submit their classification, or
after, if they ``favorite'' the subject. There is no ``back'' button: each
volunteer may only classify a given subject once. However, the presence of an
option to see what others think about any given subject before submitting your
own classification means that the classifications may not be  strictly
independent; the advantage of this system is that volunteers can learn from
others what constitutes a good lens candidate. In practice, we might expect
this to be a relatively unimportant educational resource, given the explicit
training we provide for the volunteers, which we describe in the next section.

@@

Gravitational lenses are unfamiliar objects to volunteers who are new
to the site. New volunteers need to learn what lenses look like as quickly as
possible, so that they can contribute informative classifications. They also
need to learn what lenses do not look like, in order to reduce the false
positive detection rate.

@@

More on what lenses do: inline tutorial and feedback. 
Merge into stream. Instant feedback, positive and
negative. Anecdotal support for this.

Training requires lenses to be more common than is realistic. How to manage
expectations, avoid high false positive rate? "Lenses are rare" messaging;
simulation frequency marker.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centerline{
\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}}
\caption{Screenshot of the \sw classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A screenshot of the \sw classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
\texttt{http://spacewarps.org}; the web application is written in
coffeescript, css and html and follows the general design of others written by
the Zooniverse team.\footnote{The \sw web application code is open source and
can be accessed from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The
focus of the CI is a large display of the current pre-prepared PNG image of
the ``subject'' being inspected.   When the image is clicked on by the
volunteer, a marker symbol appears where the pointer was. Several markers can
be placed.  The next image moves rapidly in from a queue formed at the right
hand side of the screen when the ``Finished marking'' button is pressed. At
the same time, the positions of the markers are written out to the
classification database, in an entry that also stores the ID of the subject,
the username (or IP address) of the volunteer, a timestamp and some other
metadata.

@@

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
features they have seen either before they submit their classification, or
after, if they ``favorite'' the subject. There is no ``back'' button: each
volunteer may only classify a given subject once. However, the presence of an
option to see what others think about any given subject before submitting your
own classification means that the classifications may not be  strictly
independent; the advantage of this system is that volunteers can learn from
others what constitutes a good lens candidate. In practice, we might expect
this to be a relatively unimportant educational resource, given the explicit
training we provide for the volunteers, which we describe in the next section.

@@

Gravitational lenses are unfamiliar objects to volunteers who are new
to the site. New volunteers need to learn what lenses look like as quickly as
possible, so that they can contribute informative classifications. They also
need to learn what lenses do not look like, in order to reduce the false
positive detection rate. There are three primary mechanisms in the \sw system
for teaching the volunteers what to look for. These are, in the order in which
they are encountered, an inline tutorial, instant feedback,
and a ``Spotter's Guide.''

\subsubsection{Inline Tutorial}

New volunteers are welcomed to the site with a very short tutorial, in which
the task is introduced, a typical image containing a simulated lens is
displayed, and the marking procedure walked through, using pop-up message
boxes. Subsequent images gradually introduce the more advanced
features of the classification interface (the QD and Talk buttons), also using
pop-up messages. The tutorial was purposely kept as short as possible so as to
provide the minimal barrier to entry.

\subsubsection{Instant Feedback}

The second image viewed after the initial tutorial image is already a survey
image, in order to get the volunteers engaged in the real task as quickly as
possible. Training continues beyond the first image tutorial through
``training subjects'' inserted randomly into the stream.  These training
subjects are either simulated lenses (known as ``sims''), or survey images
that were expert-classified (by AV, AM and PM) and found not to contain any
lens candidates (these images are known as ``duds''). The tutorial explains
that the volunteers  will be shown such training images. They are also
informed that they will receive instant feedback about their performance after
classifying (blind) any of these training subjects. Indeed, after a volunteer
finishes marking a training subject and hits ``Finished marking,'' a pop-up
message is generated, containing either positive feedback for a successful
classification (for example, ``Well done! You spotted a simulated lens,'' as
in \Fref{fig:screenshot}) or negative feedback for an unsuccessful one (for
example, ``There is no gravitational lens in this field!'')

\question{PJM}{Does the feedback lead to volunteers leaving the site more 
quickly, or less quickly? Does negative feedback have more impact than
positive?}

The initial frequency of the training images is set to be two in five;
subjects are drawn randomly from the pool of training images with this
frequency. The pool contains equal numbers of sims and duds, and the draw is
made without replacement (for that volunteer). As the number of
classifications made by a volunteer increases, this frequency is decreased, to
$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
subjects, $0.2$ for the third 20 subjects, and so on).

This training regime means that in the first 60 images viewed, each volunteer
is shown (on average) 9 simulated gravitational lenses, and 9 empty fields. 
This is a much higher rate than the natural one: to try and avoid this leading
to over-optimism among the inspectors (and a resulting high false positive
rate), we display the current ``Simulation Frequency'' on the classification
interface (``1 in 5'' in \Fref{fig:screenshot}) and maintain the consistent
theme in the feedback messages that lenses are rare.

\subsubsection{Spotter's Guide}

@@
